# Data Loading

```{r cahce=TRUE}
library(caret)
training <- read.csv("pml-training.csv", header = TRUE)
testing  <- read.csv("pml-testing.csv", header = TRUE)
```

## Summary of Data

```{r cahce=TRUE}
nrow(training)
names(training)

nrow(testing)
names(testing)

summary(training)
summary(testing)
```

# Data Preparation

## Specify column names to be used in training, and convert them to column index numbers.

```{r cahce=TRUE}
column_name <- c("roll_belt","pitch_belt","yaw_belt","total_accel_belt","gyros_belt_x",
                 "gyros_belt_y","gyros_belt_z","accel_belt_x","accel_belt_y",
                 "accel_belt_z","magnet_belt_x","magnet_belt_y","magnet_belt_z",
                 "roll_arm","pitch_arm","yaw_arm","total_accel_arm","gyros_arm_x",
                 "gyros_arm_y","gyros_arm_z","accel_arm_x","accel_arm_y","accel_arm_z",
                 "magnet_arm_x","magnet_arm_y","magnet_arm_z","roll_dumbbell",
                 "pitch_dumbbell","yaw_dumbbell","total_accel_dumbbell",
                 "gyros_dumbbell_x","gyros_dumbbell_y","gyros_dumbbell_z",
                 "accel_dumbbell_x","accel_dumbbell_y","accel_dumbbell_z",
                 "magnet_dumbbell_x","magnet_dumbbell_y","magnet_dumbbell_z",
                 "roll_forearm","pitch_forearm","yaw_forearm",
                 "total_accel_forearm",
                 "gyros_forearm_x","gyros_forearm_y","gyros_forearm_z",
                 "accel_forearm_x","accel_forearm_y","accel_forearm_z",
                 "magnet_forearm_x","magnet_forearm_y","magnet_forearm_z")

column_id <- c()
for (i in 1:length(names(training)))
{
    if ( names(training)[i] %in% column_name )
    {
        print(names(training)[i])
        column_id <- c(column_id, i)
    }
}
```

## Select columns from the data frames to be used in training, and convert them to numeric.

```{r cahce=TRUE}
for (i in 1:length(column_id))
{
    training[,column_id[i]] <- as.numeric(training[,column_id[i]])
}
for (i in 1:length(column_id))
{
    testing[,column_id[i]] <- as.numeric(testing[,column_id[i]])
}

tmpTrain <- training[, c(column_id, 160)]
names(tmpTrain)
summary(tmpTrain)

tmpTest <- testing[, c(column_id, 160)]
names(tmpTest)
summary(tmpTest)
```

# Building a model

## Building a model by Classification

```{r cahce=TRUE}
modFitCT <- train(classe ~ .,
                  data = tmpTrain, method="rpart")
modFitCT$finalModel
print(modFitCT)

plot(modFitCT$finalModel, uniform=TRUE, main="Classification Tree")
text(modFitCT$finalModel, use.n = TRUE, all = TRUE, cex = .8)
```

## Building a model by Random Forest

```{r cahce=TRUE}
modFitRF <- train(classe ~ .,
                data = tmpTrain, method="rf", prox = TRUE)
modFitRF$finalModel
print(modFitRF)

plot(modFitRF$finalModel, uniform=TRUE, main="Random Forest")
text(modFitRF$finalModel, use.n = TRUE, all = TRUE, cex = .8)
```

# Prediction

## Prediction with Classification Tree

```{r cache=TRUE}
predCT <- predict(modFitCT, tmpTest)
print(predCT)
summary(predCT)
table(training$classe, predict(modFitCT, training))
```

## Prediction wiht Random Forest

```{r cache=TRUE}
predRF <- predict(modFitRF, tmpTest)
print(predRF)
summary(predRF)
table(training$classe, predict(modFitRF, training))
```
